preprocess_sketches THU

### 2021-04-28 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
scripts to automatically merge subject logs and resave darwings

```{r}
final_subject_info = here::here('data/THU/demographics/final_subject_info.csv')
demo = read_csv(final_subject_info)
```

```{r}
drawing_path = here::here('data/THU/drawings/full_set/')
# filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
# filtered_dataset_path =  here::here('data/THU/drawings/object_drawings')
compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
# dir.create(filtered_dataset_path)
dir.create(compiled_dataset_path)
```

```{r}
all_drawings = list.files(path=drawing_path, pattern = ".png$", recursive = TRUE) %>%
    as_tibble()  %>%
    rename(fullPath = value)

@@

```{r}
practice_categories = c('triangle','this shape','this square','rectangle')

drawings_to_include <- drawing_info %>%
  left_join(demo, by=c('ID_Database')) %>%
  filter(!is.na(Age)) %>%
  mutate(age_group = floor(Age)) %>%
  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))  %>%
  filter(!category %in% practice_categories)

# copy included drawings and rename
```{r}
# file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))

file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
```

```{r}

drawings_by_category <- drawings_to_include %>%
  group_by(category, condition) %>%
  summarize(num_drawings = length(fileNameShort))

>>>>

# demographics information for subjects
```{r}
final_subject_info = here::here('data/THU/demographics/final_subject_info.csv')
demo = read_csv(final_subject_info)
```

# paths to drawings and where they should be copied
```{r}
drawing_path = here::here('data/THU/drawings/full_set/')
# these will contain tracings/drawings from all THU/CDM sessions
compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
compiled_tracing_dataset_path = here::here('data/compiled/drawings/tracings')
dir.create(compiled_dataset_path)
dir.create(compiled_tracing_dataset_path)

# old structure
# filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
# filtered_dataset_path =  here::here('data/THU/drawings/object_drawings')
# dir.create(filtered_dataset_path)
```

# grab pngs of rendered drawings
```{r}
all_drawings = list.files(path=drawing_path, pattern = ".png$", recursive = TRUE) %>%
    as_tibble()  %>%
    rename(fullPath = value)

@@

# copy tracings/drawings into separate folderes
```{r}
practice_categories = c('triangle','this shape','this square','rectangle')

drawings_to_include <- drawing_info %>%
  left_join(demo, by=c('ID_Database')) %>%
  filter(!is.na(Age)) %>%
  mutate(age_group = floor(Age)) %>%
  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))

object_drawings <- drawings_to_include %>%
  filter(!category %in% practice_categories)

tracings_to_include <- drawings_to_include %>%
  filter(category %in% practice_categories)
```

# summarize number of drawings/tracings that we had
```{r}
drawings_by_category <- object_drawings %>%
  group_by(category, condition) %>%
  summarize(num_drawings = length(fileNameShort))

tracings_by_category <- tracings_to_include %>%
  group_by(category) %>% 
  summarize(num_drawings = length(fileNameShort))
```

# copy included drawings/tracings and rename
```{r}
file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
```

```{r}
file.copy(fs::path(drawing_path, tracings_to_include$fullPath), fs::path(compiled_tracing_dataset_path, tracings_to_include$better_filename))
```
